---
title: "Assignment 3"
author: "Ruixuan Ma"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
wcgs_df <- read.csv("/Users/maruixuan/Documents/Documents/GitHub/BST650_Bootstrap/wcgs.csv", header = TRUE, stringsAsFactors = FALSE)
chol_mod <- lm(chol ~ age + weight + sbp, data = wcgs_df)

library(tidyverse)
```

## Assumption of Multiple Linear Regression

### Assumption 1: Model Errors are Normally Distributed
Overall, the residuals appear to be normally distributed, based on the histogram,
but we may have a few outliers. When we inspect the QQ-plot, we probably have an
outlier.
```{r}
str(chol_mod)
# Histogram
hist(chol_mod$residuals)

# QQ-PLOT
qqnorm(chol_mod$residuals)
```

Try a transformation:
```{r}
hist(wcgs_df$chol)
cholSq_mod <- lm(sqrt(chol) ~ age + weight + sbp, data = wcgs_df)
hist(sqrt(cholSq_mod$residuals))
qqnorm(cholSq_mod$residuals)
qqline(cholSq_mod$residuals)
```
That's probably worse. Let's leave the data alone...

### Assumtion 2: Model Errors are centered at 0
The quick and dirty way would be to look at the center of the histogram. We can
also perform a statistical test:
```{r}
t.test(chol_mod$residuals, alternative = "two.sided", mu = 0)
```
0 is dead-set in the middle of the confidence interval. We're rather confident 
that the mean of the residuals is close enough to 0.
In hypotheses test, you can say something is wrong, but you can't say something 
is true.(Maybe this is why we can just say "fail to reject h0"" but not "accept h0")

### Assumption 3: Model Errors are Homoskedastic
```{r}
par(mfrow = c(2,2))
plot(chol_mod)
# We can see from the first plot (residuals vs fitted) that there are amoset
# completely random and equal distribution of points throughout the range of x
# axis and a flat red line. So we can say that the model errors are homoskedastic.

```



### Assumption 4: Model Errors are Independent
```{r}
plot(wcgs_df$age, wcgs_df$chol)
```




### Assumption 5: Model Predictors are not Perfectly correlated
```{r}
plot(wcgs_df$age, wcgs_df$weight)
```





